---
title: "GLOBE Leadership and Society Surveys"
author: 
  - \textbf{Explore the GLOBE}
subtitle:
  - Ethan Allavarpu $\cdot$ Raymond Bai $\cdot$ Jaclyn Chiu \newline Ariel Chow $\cdot$ Carlie Lin $\cdot$ Dara Tan
date:
  - STATS 140XP $\cdot$ Fall 2021
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
output:
  beamer_presentation:
    theme: "Hannover"
    colortheme: "spruce"
    slide_level: 2
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = FALSE)
options(digits = 4)
library(knitr)
library(MASS)
library(leaps)
library(tidyverse)
library(kableExtra)
library(readxl)
library(readr)
library(reshape2)
library(stringr)
library(rworldmap)
```

# Introducing the Data
## The Data




## Exploratory Data Analysis
```{r eda_leader}
source("iso_codes.R")
col_palette <- rgb(c(0.50, 0.50, 0.00, 0.45, 0.00, 0.25, 0.75, 0.15, 0.32, 0.80),
                   c(0.50, 0.00, 0.50, 0.60, 0.00, 0.45, 0.45, 0.75, 0.25, 0.23),
                   c(0.00, 0.50, 0.50, 0.60, 0.15, 0.15, 0.00, 0.45, 0.70, 0.20),
                   alpha = 0.75)
leadership <- read.csv("GLOBE-Phase-2-Aggregated-Leadership-Data.csv")
leadership$Country.Cluster <- trimws(leadership$Country.Cluster)
society <- read.csv("GLOBE-Phase-2-Aggregated-Societal-Culture-Data.csv")
society$Country.Name[society$Country.Name == "IRAN"] <- "Iran"
society$Country.Cluster <- trimws(society$Country.Cluster)
combined_data <- full_join(leadership, society,
                           by = c("Country", "Country.Name", "Country.Cluster"))
countries <- data.frame("country" = leadership$Country.Name)
iso_codes <- as.data.frame(iso_codes)
names(iso_codes) <- c("code", "country")
country_codes <- countries %>% left_join(iso_codes)
country_codes[is.na(country_codes$code), "code"] <- c("GBR", "CZE", "VEN",
                                                      "IRN", "RUS", "KOR",
                                                      "ZAF", "BOL", "CHE",
                                                      "ZAF", "CAN", "DEU",
                                                      "DEU", "USA")
combined_data <- combined_data %>% mutate("Code" = country_codes$code)
colnames(combined_data) <- vapply(colnames(combined_data),
                                  function(x){ gsub(pattern = "[\\.]+",
                                                    replacement = " ", x)},
                                  character(1))
mapped_data <- joinCountryData2Map(combined_data, nameJoinColumn = "Code")
par(mai = rep(0.95, 4), xaxs = "i", yaxs = "i")
# Edit the following function to create maps for different variables
# nameColumnToPlot should be the variable name
# numCats defines how many breaks you want (44 is the maximum)
# colourPalette defines the range of colors to plot
## alpha in rgb() is the transparency factor
### Edit the from and to arguments to match the variable of interest
### Divide by the maximum value of the variable of interest
# Autocratic Scores by Country and Country Cluster ----
mapCountryData(mapped_data, nameColumnToPlot = "Autocratic",
               numCats = 43,
               colourPalette = rgb(0.5, 0, 0,
                                   alpha = seq(from = 1, to = 7,
                                               length.out = 43) / 7),
               borderCol = "black",
               missingCountryCol = rgb(0, 0, 0, alpha = 0.5),
               mapTitle = "Autocratic Levels by Country")
```

## Exploratory Data Analysis

```{r eda_social}
culture <- read_csv('GLOBE-Phase-2-Aggregated-Societal-Culture-Data.csv')
colors <- c('#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b',
            '#e377c2', '#7f7f7f', '#bcbd22', '#17becf')
spv <- culture %>%
  select(country = 'Country', country_name = 'Country Name',
         country_cluster = 'Country Cluster', contains('Practices')) %>%
  pivot_longer(contains('Practices'), values_to = 'practice') %>%
  mutate(name = str_replace_all(name, ' Societal Practices', '')) %>%
  full_join(culture %>%
              select(country = 'Country', country_name = 'Country Name',
                     country_cluster = 'Country Cluster', contains('Values')) %>%
              pivot_longer(contains('Values')) %>%
              mutate(name = str_replace_all(name, ' Societal Values', ''),
                     name = str_replace(name, 'Human', 'Humane')),
            by = c('country', 'country_name', 'country_cluster', 'name')) %>%
  filter(!is.na(country_cluster))
change_name <- !is.na(str_extract(spv$name, "(?<=\\().+(?=\\))"))
spv$name[change_name] <- str_extract(spv$name, "(?<=\\().+(?=\\))")[change_name]
ggplot(spv) +
  geom_point(aes(practice, value, color = country_cluster),
             cex = 1.5, alpha = 0.65) +
  scale_color_manual(values = colors, name = 'Country Cluster') +
  labs(title = 'Values vs. Practices by Cultural Dimension and Country Cluster',
       caption = 'Note: Countries with missing country clusters were excluded.',
       x = 'Societal Practices', y = 'Societal Values') +
  theme_bw() +
  facet_wrap(~ name, nrow = 3, scales = 'free') + 
  theme(strip.text.x = element_text(size = 14))
```


## Problem Statements

  1. Which characteristics or traits do countries tend to group together when determining "good" leadership values?
      - Which countries have similar perceptions of these leadership values?

  2. Do societal practices and societal values align? 
      - If they do not, which practices and values deviate most significantly?

# Analysis

## Leadership Clusters: Characteristics
```{r pca, out.width="70%"}
col_palette <- rgb(c(0.50, 0.50, 0.00, 0.45, 0.00, 0.25, 0.75, 0.15, 0.32, 0.80),
                   c(0.50, 0.00, 0.50, 0.60, 0.00, 0.45, 0.45, 0.75, 0.25, 0.23),
                   c(0.00, 0.50, 0.50, 0.60, 0.15, 0.15, 0.00, 0.45, 0.70, 0.20),
                   alpha = 0.75)

leadership <- read.csv("GLOBE-Phase-2-Aggregated-Leadership-Data.csv")
leadership$Country.Cluster <- trimws(leadership$Country.Cluster)
countries <- data.frame("country" = leadership$Country.Name)
iso_codes <- as.data.frame(iso_codes)
names(iso_codes) <- c("code", "country")
country_codes <- countries %>% left_join(iso_codes)
country_codes[is.na(country_codes$code), "code"] <- c("GBR", "CZE", "VEN",
                                                      "IRN", "RUS", "KOR",
                                                      "ZAF", "BOL", "CHE",
                                                      "ZAF", "CAN", "DEU",
                                                      "DEU", "USA")
leadership <- leadership %>% mutate("Code" = country_codes$code)
rename_columns <- function(x) {
  new_name <- gsub(pattern = "[\\.]+", replacement = " ", x)
  new_name <- gsub(pattern = "Originally Labeled _", replacement = "(", new_name)
  gsub(pattern = "_", replacement = ")", new_name)
}
colnames(leadership) <- vapply(colnames(leadership), rename_columns, character(1))
leadership <- leadership %>% dplyr::select(-Country)
leadership <- leadership[, is.na(str_match(names(leadership),
                                           "Global Leadership Dimension"))]
# PCA
num_data <- leadership[, vapply(leadership, is.numeric, logical(1))]
rownames(num_data) <- leadership$`Country Name`
change_names <- str_extract_all(colnames(num_data),"(?<=[:digit:] ).*")
colnames(num_data)[vapply(change_names, length, numeric(1)) > 0] <- unlist(change_names)
pca <- prcomp(num_data)

# Cluster the leadership characteristics
pca4 <- pca$rotation[, 1:4]
set.seed(0)
w_ss <- numeric(20)
k_clust <- list()
length(k_clust) <- 20
for (k in seq_along(w_ss)) {
  k_clusters <- kmeans(pca4, centers = k, nstart = 20)
  k_clust[[k]] <- k_clusters
  w_ss[k] <- k_clusters$tot.withinss
}
## k = 5 seems best, but k = 3 provides more relevant groups
cols <- rgb(c(0.25, 0.50, 0.00), c(0.50, 0.00, 0.50), c(0.00, 0.50, 0.50),
            alpha = 0.75)[sort(k_clust[[3]]$cluster)]
names(cols) <- names(sort(k_clust[[3]]$cluster))
```
```{r pca_heatmap}
pca4 <- pca4[names(cols), ]
melt(pca4) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(low = rgb(0.5, 0, 0, alpha = 1),
                       high = rgb(0, 0.5, 0, alpha = 1),
                       mid = "white",
                       midpoint = 0, space = "Lab",
                       name = "PCA Coefficient") +
  labs(title = "PCA Coefficients for Each Variable",
       x = "Variable", y = "Principal Component Number",
       caption = "Note: Variables colored by cluster") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1),
        axis.text.y = element_text(color = cols, size = 12)) +
  coord_flip()
```

## Leadership Clusters: Countries

```{r kmeans}
# Use first four principal components for clustering
pca_x <- pca$x[, 1:4]
set.seed(85)
w_ss <- numeric(30)
k_clust <- list()
length(k_clust) <- 30
for (k in seq_along(w_ss)) {
  k_clusters <- kmeans(pca_x, centers = k, nstart = 20)
  k_clust[[k]] <- k_clusters
  w_ss[k] <- k_clusters$tot.withinss
}

## 4 clusters appears to be the best
best_4 <- k_clust[[4]]
leadership <- mutate(leadership, "Similar Values" = factor(best_4$cluster), "Code" = country_codes$code)

# K-means Clusters and Leadership Values ----
mapped_data <- joinCountryData2Map(leadership, nameJoinColumn = "Code")
mapCountryData(mapped_data, nameColumnToPlot = "Similar Values",
               numCats = 4, catMethod = "categorical",
               colourPalette = col_palette[seq_len(4) + 3],
               borderCol = "black",
               missingCountryCol = rgb(0, 0, 0, alpha = 0.5),
               mapTitle = "Country Clusters with Similar Leadership Values",
               addLegend = FALSE)
```


## Societal Values vs. Practices
```{r SPV Plots}
leadership <- read_csv('GLOBE-Phase-2-Aggregated-Leadership-Data.csv')
culture <- read_csv('GLOBE-Phase-2-Aggregated-Societal-Culture-Data.csv')
colors <- c('#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b',
            '#e377c2', '#7f7f7f', '#bcbd22', '#17becf')

spv <- culture %>%
  select(country = 'Country', country_name = 'Country Name',
         country_cluster = 'Country Cluster', contains('Practices')) %>%
  pivot_longer(contains('Practices'), values_to = 'practice') %>%
  mutate(name = str_replace_all(name, ' Societal Practices', '')) %>%
  full_join(culture %>%
              select(country = 'Country', country_name = 'Country Name',
                     country_cluster = 'Country Cluster', contains('Values')) %>%
              pivot_longer(contains('Values')) %>%
              mutate(name = str_replace_all(name, ' Societal Values', ''),
                     name = str_replace(name, 'Human', 'Humane')),
            by = c('country', 'country_name', 'country_cluster', 'name')) %>%
  filter(!is.na(country_cluster))

change_name <- !is.na(str_extract(spv$name, "(?<=\\().+(?=\\))"))
spv$name[change_name] <- str_extract(spv$name, "(?<=\\().+(?=\\))")[change_name]
get_spv_slr <- function(n) {
  model <- lm(practice ~ value, data = spv %>% filter(name == n))
  results <- summary(model)$coefficients['value', ]
  tibble(name = n, coefficient = unname(results['Estimate']),
         p_value = unname(results['Pr(>|t|)']))
}
slr_results <- map_df(unique(spv$name), get_spv_slr) %>%
  arrange(p_value)
alpha <- 0.05 / nrow(slr_results)
```

```{r SPV SLR Table, results=TRUE}
significant <- slr_results$p_value < alpha
kable(slr_results, col.names = c('Cultural Dimension', 'Coefficient Value',
                                 'p-value'), booktabs = TRUE,
      caption = 'Results of Simple Linear Regression by Cultural Dimension') %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(which(significant), background = '#E5F5E0') %>%
  row_spec(which(!significant)[c(FALSE, TRUE)], background = '#F0F0F0')
```

# Conclusions

## Leadership Clusters

## Societal Values vs. Practices

# Limitations

# Further Research
