---
title: "GLOBE Leadership and Society Surveys"
author: 
  - \textbf{Explore the GLOBE}
subtitle:
  - Ethan Allavarpu $\cdot$ Raymond Bai $\cdot$ Jaclyn Chiu \newline Ariel Chow $\cdot$ Carlie Lin $\cdot$ Dara Tan
date:
  - STATS 140XP $\cdot$ Fall 2021
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
output:
  beamer_presentation:
    theme: "Hannover"
    colortheme: "spruce"
    slide_level: 2
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = FALSE)
options(digits = 4)
library(knitr)
library(MASS)
library(leaps)
library(tidyverse)
library(kableExtra)
library(readxl)
library(readr)
library(reshape2)
library(stringr)
library(rworldmap)
```

# Introducing the Data
## The Data

  - GLOBE (Global Leadership & Organizational Behavior Effectiveness)
    - Goal: Identify the relationships between various leadership and societal characteristics
    - Over 17,000 middle managers, 62 cultures
    - Survey from 1 (negative) to 7 (positive)
  - Outside source: ISO Codes from Wikipedia
    - Uniform identifiers for countries for visualization purposes
    



## Exploratory Data Analysis
```{r eda_leader}
source("iso_codes.R")
col_palette <- rgb(c(0.50, 0.50, 0.00, 0.45, 0.00, 0.25, 0.75, 0.15, 0.32, 0.80),
                   c(0.50, 0.00, 0.50, 0.60, 0.00, 0.45, 0.45, 0.75, 0.25, 0.23),
                   c(0.00, 0.50, 0.50, 0.60, 0.15, 0.15, 0.00, 0.45, 0.70, 0.20),
                   alpha = 0.75)
leadership <- read.csv("GLOBE-Phase-2-Aggregated-Leadership-Data.csv")
leadership$Country.Cluster <- trimws(leadership$Country.Cluster)
society <- read.csv("GLOBE-Phase-2-Aggregated-Societal-Culture-Data.csv")
society$Country.Name[society$Country.Name == "IRAN"] <- "Iran"
society$Country.Cluster <- trimws(society$Country.Cluster)
combined_data <- full_join(leadership, society,
                           by = c("Country", "Country.Name", "Country.Cluster"))
countries <- data.frame("country" = leadership$Country.Name)
iso_codes <- as.data.frame(iso_codes)
names(iso_codes) <- c("code", "country")
country_codes <- countries %>% left_join(iso_codes)
country_codes[is.na(country_codes$code), "code"] <- c("GBR", "CZE", "VEN",
                                                      "IRN", "RUS", "KOR",
                                                      "ZAF", "BOL", "CHE",
                                                      "ZAF", "CAN", "DEU",
                                                      "DEU", "USA")
combined_data <- combined_data %>% mutate("Code" = country_codes$code)
colnames(combined_data) <- vapply(colnames(combined_data),
                                  function(x){ gsub(pattern = "[\\.]+",
                                                    replacement = " ", x)},
                                  character(1))
mapped_data <- joinCountryData2Map(combined_data, nameJoinColumn = "Code")
par(mai = rep(0.95, 4), xaxs = "i", yaxs = "i")
# Edit the following function to create maps for different variables
# nameColumnToPlot should be the variable name
# numCats defines how many breaks you want (44 is the maximum)
# colourPalette defines the range of colors to plot
## alpha in rgb() is the transparency factor
### Edit the from and to arguments to match the variable of interest
### Divide by the maximum value of the variable of interest
# Autocratic Scores by Country and Country Cluster ----
mapCountryData(mapped_data, nameColumnToPlot = "Autocratic",
               numCats = 43,
               colourPalette = rgb(0.5, 0, 0,
                                   alpha = seq(from = 1, to = 7,
                                               length.out = 43) / 7),
               borderCol = "black",
               missingCountryCol = rgb(0, 0, 0, alpha = 0.5),
               mapTitle = "Autocratic Levels by Country")
```

## Exploratory Data Analysis

```{r eda_social}
culture <- read_csv('GLOBE-Phase-2-Aggregated-Societal-Culture-Data.csv')
colors <- c('#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b',
            '#e377c2', '#7f7f7f', '#bcbd22', '#17becf')
spv <- culture %>%
  select(country = 'Country', country_name = 'Country Name',
         country_cluster = 'Country Cluster', contains('Practices')) %>%
  pivot_longer(contains('Practices'), values_to = 'practice') %>%
  mutate(name = str_replace_all(name, ' Societal Practices', '')) %>%
  full_join(culture %>%
              select(country = 'Country', country_name = 'Country Name',
                     country_cluster = 'Country Cluster', contains('Values')) %>%
              pivot_longer(contains('Values')) %>%
              mutate(name = str_replace_all(name, ' Societal Values', ''),
                     name = str_replace(name, 'Human', 'Humane')),
            by = c('country', 'country_name', 'country_cluster', 'name')) %>%
  filter(!is.na(country_cluster))
change_name <- !is.na(str_extract(spv$name, "(?<=\\().+(?=\\))"))
spv$name[change_name] <- str_extract(spv$name, "(?<=\\().+(?=\\))")[change_name]
ggplot(spv) +
  geom_point(aes(practice, value, color = country_cluster),
             cex = 1.5, alpha = 0.65) +
  scale_color_manual(values = colors, name = 'Country Cluster') +
  labs(title = 'Values vs. Practices by Cultural Dimension and Country Cluster',
       caption = 'Note: Countries with missing country clusters were excluded.',
       x = 'Societal Practices', y = 'Societal Values') +
  theme_bw() +
  facet_wrap(~ name, nrow = 3, scales = 'free') + 
  theme(strip.text.x = element_text(size = 14))
```


## Problem Statements

  1. Which characteristics or traits do countries tend to group together when determining "good" leadership values?
      - Which countries have similar perceptions of these leadership values?

  2. Do societal practices and societal values align? 
      - If they do not, which practices and values deviate most significantly?

# Analysis

## Leadership Clusters: Methodology

  1. Remove second-order factor analysis variables (difficult for interpretation)
  
  2. Perform PCA on the remaining numeric variables
  
  3. Perform $k$-means clustering on the first four principal components for both characteristics and countries
      - Choose first four PCs because they explain around 80% of the variation
    
## Leadership Clusters: Methodology
```{r leader_methods, fig.height=8}
plot(seq_len(10), axes = FALSE, xlab = "", ylab = "", type = "n")
symbols(x = c(5, 2.5, 7.5),
        y = c(7.5, 2.5, 2.5),
        rectangles = matrix(c(3, 1.5,
                              3, 1.5,
                              3, 1.5),
                            nrow = 3,
                            byrow = TRUE),
        inches = FALSE, add = TRUE)
text(x = 5, y = 9, labels = "Methodology for Leadership Analysis", cex = 2.5)
text(x = c(5, 2.5, 7.5),
     y = c(7.5, 2.5, 2.5),
     labels = c("PCA",
                "k-means on characteristics",
                "k-means on countries"), cex = c(2, 1.25, 1.25))
arrows(x0 = 5, y0 = 7.5 - 1.5 / 2,
       x1 = c(2.5, 7.5), y1 = 2.5 + 1.5 / 2,
       length = 0.1, angle = 25)
text(3.5, 5.25, "Use first four PCs", srt = 45, cex = 1.25)
text(6.5, 5.25, "Use first four PCs", srt = 360 - 45, cex = 1.25)
```


## Leadership Clusters: Characteristics
```{r pca, out.width="70%"}
col_palette <- rgb(c(0.50, 0.50, 0.00, 0.45, 0.00, 0.25, 0.75, 0.15, 0.32, 0.80),
                   c(0.50, 0.00, 0.50, 0.60, 0.00, 0.45, 0.45, 0.75, 0.25, 0.23),
                   c(0.00, 0.50, 0.50, 0.60, 0.15, 0.15, 0.00, 0.45, 0.70, 0.20),
                   alpha = 0.75)

leadership <- read.csv("GLOBE-Phase-2-Aggregated-Leadership-Data.csv")
leadership$Country.Cluster <- trimws(leadership$Country.Cluster)
countries <- data.frame("country" = leadership$Country.Name)
iso_codes <- as.data.frame(iso_codes)
names(iso_codes) <- c("code", "country")
country_codes <- countries %>% left_join(iso_codes)
country_codes[is.na(country_codes$code), "code"] <- c("GBR", "CZE", "VEN",
                                                      "IRN", "RUS", "KOR",
                                                      "ZAF", "BOL", "CHE",
                                                      "ZAF", "CAN", "DEU",
                                                      "DEU", "USA")
leadership <- leadership %>% mutate("Code" = country_codes$code)
rename_columns <- function(x) {
  new_name <- gsub(pattern = "[\\.]+", replacement = " ", x)
  new_name <- gsub(pattern = "Originally Labeled _", replacement = "(", new_name)
  gsub(pattern = "_", replacement = ")", new_name)
}
colnames(leadership) <- vapply(colnames(leadership), rename_columns, character(1))
leadership <- leadership %>% dplyr::select(-Country)
leadership <- leadership[, is.na(str_match(names(leadership),
                                           "Global Leadership Dimension"))]
# PCA
num_data <- leadership[, vapply(leadership, is.numeric, logical(1))]
rownames(num_data) <- leadership$`Country Name`
change_names <- str_extract_all(colnames(num_data),"(?<=[:digit:] ).*")
colnames(num_data)[vapply(change_names, length, numeric(1)) > 0] <- unlist(change_names)
pca <- prcomp(num_data)

# Cluster the leadership characteristics
pca4 <- pca$rotation[, 1:4]
set.seed(0)
w_ss <- numeric(20)
k_clust <- list()
length(k_clust) <- 20
for (k in seq_along(w_ss)) {
  k_clusters <- kmeans(pca4, centers = k, nstart = 20)
  k_clust[[k]] <- k_clusters
  w_ss[k] <- k_clusters$tot.withinss
}
## k = 5 seems best, but k = 3 provides more relevant groups
cols <- rgb(c(0.25, 0.50, 0.00), c(0.50, 0.00, 0.50), c(0.00, 0.50, 0.50),
            alpha = 0.75)[sort(k_clust[[3]]$cluster)]
names(cols) <- names(sort(k_clust[[3]]$cluster))
```
```{r pca_heatmap}
pca4 <- pca4[names(cols), ]
melt(pca4) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(low = rgb(0.5, 0, 0, alpha = 1),
                       high = rgb(0, 0.5, 0, alpha = 1),
                       mid = "white",
                       midpoint = 0, space = "Lab",
                       name = "PCA Coefficient") +
  labs(title = "PCA Coefficients for Each Variable",
       x = "Variable", y = "Principal Component Number",
       caption = "Note: Variables colored by cluster") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1),
        axis.text.y = element_text(color = cols, size = 12)) +
  coord_flip()
```

## Leadership Clusters: Characteristics
	
\definecolor{clust3}{HTML}{408000}
\definecolor{clust2}{HTML}{800080}
\definecolor{clust1}{HTML}{008080}

  1. \textcolor{clust1}{Internally competitive, malevolent, status conscious, self-centred, bureaucratic, face saver, autocratic}
  
      - Negative characteristics
    
  2. \textcolor{clust2}{Humane-oriented, modesty}
  
      - Distinctly different group of two
  
  3. \textcolor{clust3}{Participative, team integrator, inspirational, autonomous, administratively competent, integrity, visionary, diplomatic, decisive, collaborative team orientation, self-sacrifice, performance-oriented}
  
      - Positive characteristics
  

## Leadership Clusters: Countries
```{r kmeans}
# Use first four principal components for clustering
pca_x <- pca$x[, 1:4]
set.seed(85)
w_ss <- numeric(30)
k_clust <- list()
length(k_clust) <- 30
for (k in seq_along(w_ss)) {
  k_clusters <- kmeans(pca_x, centers = k, nstart = 20)
  k_clust[[k]] <- k_clusters
  w_ss[k] <- k_clusters$tot.withinss
}

## 4 clusters appears to be the best
best_4 <- k_clust[[4]]
leadership <- mutate(leadership, "Similar Values" = factor(best_4$cluster), "Code" = country_codes$code)

# K-means Clusters and Leadership Values ----
mapped_data <- joinCountryData2Map(leadership, nameJoinColumn = "Code")
mapCountryData(mapped_data, nameColumnToPlot = "Similar Values",
               numCats = 4, catMethod = "categorical",
               colourPalette = col_palette[seq_len(4) + 3],
               borderCol = "black",
               missingCountryCol = rgb(0, 0, 0, alpha = 0.5),
               mapTitle = "K-Means Clustering (k = 4) on the First Four Principal Components",
               addLegend = FALSE)
```

*Note: East, West Germany in the same cluster. South Africa colored by Black sample (rather than the White sample)*

## Leadership Clusters: Countries

\definecolor{clust4}{HTML}{739999}
\definecolor{clust5}{HTML}{000026}
\definecolor{clust6}{HTML}{407326}
\definecolor{clust7}{HTML}{BF7300}

  - \textcolor{clust4}{Light Blue}: Latin America, Mediterranean
  - \textcolor{clust5}{Dark Blue}: Asia
  - \textcolor{clust6}{Green}: No specific regionality
  - \textcolor{clust7}{Gold}: Western and Northern Europe, Anglo

## Leadership Clusters
```{r cluster_values}
characteristic_values <- sapply(num_data, FUN = function(x) {
  tapply(X = x, INDEX = leadership$`Similar Values`, FUN = median)
  })
cols <- cols[colnames(characteristic_values)]
cols <- cols[apply(characteristic_values, 2, mean) %>% order()]
characteristic_values <- characteristic_values[, apply(characteristic_values,
                                                       2, mean) %>% order()]
melt(characteristic_values) %>%
  ggplot(aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(low = rgb(0.5, 0, 0, alpha = 1),
                       high = rgb(0, 0.5, 0, alpha = 1),
                       midpoint = 4, space = "Lab",
                       name = "Median Survey Score") +
  labs(title = "Median Leadership Category Scores by Cluster",
       x = "Cluster", y = "Leadership Category") +
  theme_minimal() +
  theme(axis.text.x = element_text(color = col_palette[seq_len(4) + 3]),
        axis.text.y = element_text(color = cols, size = 8))
```

## Societal Values vs. Practices: Methodology

For each cultural dimension:

- Simple linear regression model: $y = \beta_0 + \beta_1 x$

- $t$-test: $H_0: \beta_1 = 0$ versus $H_1: \beta_1 \ne 0$

- Bonferroni Correction

  - Change significance threshold from $\alpha = 0.05$ to $\alpha = \frac{0.05}{9} \approx `r round(0.05 / 9, 4)`$

## Societal Values vs. Practices: Findings

```{r SPV Plots}
leadership <- read_csv('GLOBE-Phase-2-Aggregated-Leadership-Data.csv')
culture <- read_csv('GLOBE-Phase-2-Aggregated-Societal-Culture-Data.csv')
colors <- c('#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b',
            '#e377c2', '#7f7f7f', '#bcbd22', '#17becf')

spv <- culture %>%
  select(country = 'Country', country_name = 'Country Name',
         country_cluster = 'Country Cluster', contains('Practices')) %>%
  pivot_longer(contains('Practices'), values_to = 'practice') %>%
  mutate(name = str_replace_all(name, ' Societal Practices', '')) %>%
  full_join(culture %>%
              select(country = 'Country', country_name = 'Country Name',
                     country_cluster = 'Country Cluster', contains('Values')) %>%
              pivot_longer(contains('Values')) %>%
              mutate(name = str_replace_all(name, ' Societal Values', ''),
                     name = str_replace(name, 'Human', 'Humane')),
            by = c('country', 'country_name', 'country_cluster', 'name')) %>%
  filter(!is.na(country_cluster))

change_name <- !is.na(str_extract(spv$name, "(?<=\\().+(?=\\))"))
spv$name[change_name] <- str_extract(spv$name, "(?<=\\().+(?=\\))")[change_name]
get_spv_slr <- function(n) {
  model <- lm(practice ~ value, data = spv %>% filter(name == n))
  results <- summary(model)$coefficients['value', ]
  tibble(name = n, coefficient = unname(results['Estimate']),
         p_value = unname(results['Pr(>|t|)']))
}
slr_results <- map_df(unique(spv$name), get_spv_slr) %>%
  arrange(p_value)
alpha <- 0.05 / nrow(slr_results)
```

```{r SPV SLR Table, results=TRUE}
significant <- slr_results$p_value < alpha
kable(slr_results, col.names = c('Cultural Dimension', 'Coefficient Value',
                                 'p-value'), booktabs = TRUE,
      caption = 'Results of Simple Linear Regression by Cultural Dimension') %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(which(significant), background = '#E5F5E0') %>%
  row_spec(which(!significant)[c(FALSE, TRUE)], background = '#F0F0F0')
```

# Conclusions

## Leadership Clusters

\definecolor{clust2}{HTML}{800080}
\definecolor{clust6}{HTML}{407326}

  - Characteristics clustered largely on negative or positive connotations
    - Exceptions: \textcolor{clust2}{Humane oriented, modesty}
  - Countries clustered heavily on geographic region
    - Exceptions: \textcolor{clust6}{Green cluster}

## Societal Values vs. Practices

  - Practices do not align
    - Correlations often negative
  - Consider how this might affect policy implementation
  
## Further Research

  - Investigate how other indices (e.g., freedom index, happiness index, government approval ratings) explain groupings for leadership values
  - Potential causes behind inverse relationship between societal values and practices
    - Are people valuing certain things *because* they aren't present in the society?
  - Expand the survey to more countries to see if regional trends/clusters remain

## Limitations

  - Only 62 cultures observed
  - Some countries split
    - Germany: East vs. West (possibly related to Berlin Wall)
    - South Africa: White vs. Black (possibly related to Apartheid)
  - Data appears to be from 15+ years ago
    - Potentially outdated information
    - May consider a resurvey
  - Unsure of how second-order factor analysis performed
  - No "official" codebook--just found the survey questions
