---
title: "K-Nearest Neighbors (KNN)"
author: 
  - Ethan Allavarpu $\cdot$ Raymond Bai $\cdot$ Jaclyn Chiu \newline Ariel Chow $\cdot$ Carlie Lin $\cdot$ Dara Tan \newline \textbf{Explore the GLOBE}
subtitle:
  - STATS 140XP Teaching Video
date: |
  | Fall 2021
output:
  beamer_presentation:
    theme: "CambridgeUS"
    colortheme: "rose"
    slide_level: 1
header-includes:
  - \setbeamertemplate{footline}{}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      out.height = "90%")
library(tidyverse)
```

# What is KNN?

  - KNN: K-nearest neighbors
  - Classification method to predict a certain response
  - Numeric predictor variables (distance)
  
# The Algorithm

  - Standardize variables to be on the same scale
  - Calculate the $k$ nearest observations by distance
  - Find the response values of those observations
  - Assign the new point's response value to the most common of the $k$ neighbors
  
# An Example

```{r}
set.seed(3)
x <- runif(n = 7, min = -2, max = 6)
y <- runif(n = 7, min = 0, max = 5)
train <- cbind(x, y)
train_col <- sample(x = rgb(c(0.5, 0), 0, c(0, 0.5), alpha = 0.75),
                    size = nrow(train),
                    replace = TRUE)
test <- c(1.5, 3)
distance <- function(a, b) {
  sqrt(sum((a - b)^2))
}
test_dists <- apply(train, 1, distance, b = test)
plot(train, pch = 19, col = train_col, cex = 2, asp = 1, las = 1)
```

# A New Observation

```{r}
plot(train, pch = 19, col = train_col, cex = 2, asp = 1, las = 1)
points(x = test[1], y = test[2], pch = 19, col = "black", cex = 3)
```

# $k = 1$

```{r}
plot(train, pch = 19, col = train_col, cex = 2, asp = 1, las = 1)
points(x = test[1], y = test[2], pch = 19,
       col = max(train_col[which.min(test_dists)]), cex = 2)
symbols(x = test[1], y = test[2], circles = min(test_dists),
        inches = FALSE, add = TRUE)
segments(x0 = test[1], y0 = test[2],
         x1 = train[which.min(test_dists), 1],
         y1 = train[which.min(test_dists), 2])
text(x = 1.75, y = 1, labels = "Blue", col = max(train_col[which.min(test_dists)]),
     cex = 3)
```

# $k = 3$

```{r}
plot(train, pch = 19, col = train_col, cex = 2, asp = 1, las = 1)
points(x = test[1], y = test[2], pch = 19,
       col = names(which.max(table(train_col[order(test_dists)[1:3]]))),
       cex = 3)
symbols(x = test[1], y = test[2], circles = sort(test_dists)[3],
        inches = FALSE, add = TRUE)
segments(x0 = test[1], y0 = test[2],
         x1 = train[order(test_dists)[1:3], 1],
         y1 = train[order(test_dists)[1:3], 2])
text(x = 1.75, y = 1, labels = "Red",
     col = names(which.max(table(train_col[order(test_dists)[1:3]]))), cex = 3)
```

# $k = 5$

```{r}
plot(train, pch = 19, col = train_col, cex = 2, asp = 1, las = 1)
points(x = test[1], y = test[2], pch = 19,
       col = names(which.max(table(train_col[order(test_dists)[1:5]]))),
       cex = 3)
symbols(x = test[1], y = test[2], circles = sort(test_dists)[5],
        inches = FALSE, add = TRUE)
segments(x0 = test[1], y0 = test[2],
         x1 = train[order(test_dists)[1:5], 1],
         y1 = train[order(test_dists)[1:5], 2])
text(x = 1.75, y = 1, labels = "Blue",
     col = names(which.max(table(train_col[order(test_dists)[1:5]]))), cex = 3)
```

# $k = 7$

```{r}
plot(train, pch = 19, col = train_col, cex = 2, asp = 1, las = 1)
points(x = test[1], y = test[2], pch = 19,
       col = names(which.max(table(train_col[order(test_dists)[1:7]]))),
       cex = 3)
symbols(x = test[1], y = test[2], circles = sort(test_dists)[7],
        inches = FALSE, add = TRUE)
segments(x0 = test[1], y0 = test[2],
         x1 = train[order(test_dists)[1:7], 1],
         y1 = train[order(test_dists)[1:7], 2])
text(x = 1.75, y = 1, labels = "Blue",
     col = names(which.max(table(train_col[order(test_dists)[1:7]]))), cex = 3)
```




